### 2016-12-01 ms/ms.tex
updated cover letter, ms

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage[numbers]{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{times}
\usepackage{textcomp}
\usepackage{xr}
\usepackage{etoolbox}
\usepackage{filecontents}
\usepackage{url}
\usepackage{rotating}
\externaldocument{SI}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

@@

\def\title{Major interaction reorganizations punctuate the assembly of
  pollination networks} \def\author{Lauren C.\ Ponisio$^{1,2,3}$,
  Marilia P. Gaiarsa$^4$, Claire Kremen$^1$}

\def\runninghead{Plant-pollinator network assembly}
\def\keywords{community assembly, change points, specialization,
  nestedness, modularity, bipartite, preferential attachment}

\def\extras{
  \begin{itemize}
  \item Submitted as a Letter
  \item Abstract word count: 148
  \item Main text word count: 5152
  \item Number of references: 65
  \item Number of figures: 6
  \item Author contributions: CK designed the study, LCP and CK
    collected data, LCP and MPG analyzed output data.  LCP wrote the
    first draft of the manuscript, and all authors contributed to
    revisions.
  \item Data accessibility statement: Data will de depositied in Dryad
    upon publication
  \end{itemize}
}

@@

\begin{abstract}  
 % The ability of communities to maintain function in the face of
  %species extinction is related to the structure of networks. Lauren - i changed the phrasing because structure of network and network structure were too close.
  The structure of interaction networks is related to the ability of communities to maintain function in the face of
  species extinction. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations.%  In contrast, the
  % non-assembling networks did not restructure as frequently.
  % Across all communities, pollinator species were opportunistic in the
  % flowers they visited.
   Generalist species were the most persistent and 
also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. % High
  % species and interaction turnover was ubiquitous across assembling
  % and non-assembling communities, though unique interactions turned
  % over at higher rates in assembling hedgerows as the networks
  % continually reorganized.
  % Nestedness of assembling networks also increased through time, but
  The sensitivity of networks to cascading perturbations,
  increased with assembly, at least partially due to accumulating
  species richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration --- challenging
  the widely-held hypothesis that mutualistic networks assemble
  through preferential attachment.
\end{abstract}

@@

%% introduce mutualisms, restoration, network assembly
Global change has created a severe biodiversity crisis, and as species
are lost, so are their interactions \citep{dunn2009sixth,
  barnosky2011has}. Because mutualistic interactions are essential for
maintaining the diversity of their component guilds, these systems are
particularly at risk from coextinction cascades. The nature of these
cascades will depend on the interaction patterns within a community
\citep{Memmott2004, Rezende2007, Bascompte2009, Thebault2010}. To
safeguard ecological function, it has become increasingly imperative
to aid the recovery of lost interactions and component biodviersity
through ecological restoration, and a key restoration aim is to
facilitate assembly of robust interaction networks
\citep{menz-2010-4}. We know little, however, about how to re-assemble
interacting communities through restoration, or the process of
ecological network assembly more generally.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[the ``rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that phenologically new plant and pollinator species tended to
interact with already well-connected species, potentially because
these species are either more abundant or more temporally
persistent. In addition, using a space-for-time substitution to study
primary succession along a glacier foreland, \cite{albrecht2010plant}
also found some evidence that assembly occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}.  An
increase in nestedness could result from the preferential attachment
process where specialist species attach to the well-connected,
generalist core.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks that respond to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}. In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts that pollinators
optimize their use of floral resources to reduce interspecific
competition and improve resource-use efficiency
\citep{pyke1984optimal, valdovinos2010consequences,
  valdovinos2013adaptive, albrecht2010plant, Bluthgen2007}. No
studies, however, have examined whether network changing points occur
during ecological network assembly, and how these changes relate to
the species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially ``applied succession''
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. To ensure the continued provision
of ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, kremen-2015-602, ponisio2015farm}, and
promote the persistence and colonization of floral resource
specialists \citep{mgonigle-2015-x}. It is important to understand how
these new species are being incorporated into the network as the
community assembles, and the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator community assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a build
up of interactions as would be predicted by preferential attachment,
or instead is punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven by peripheral, temporally variable species while a
stable, well-connected core of species persist. We test whether the
species that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less
persistent and connected species. To further explore the mechanisms
underlying the temporal dynamics of the networks, we examine patterns
in the species and interaction temporal turnover. Lastly, we
investigate whether networks are assembling toward predictable
interaction patterns, and the ramifications for the robustness of the
networks to species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of independent
assembling hedgerows communities (N=5), and of two types of
non-assembling communities to serve as controls: unrestored, weedy
field margins (N=19) and mature hedgerows (greater than 10 years since
planting, N=29). The sites were located in the Central Valley of
California in Yolo, Colusa and Solano Counties. This area is composed
of intensively managed agriculture --- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows are ca.~3--6
m wide and approximately 350 m long, bordering large (ca.\
30--hectare) crop fields. Hedgerows consist of native, perennial,
shrub and tree plantings including \textit{Rosa californica},
\textit{Cercis occidentalis}, \textit{Ceanothus spp.},
\textit{Heteromeles arbutifolia}, \textit{Sambucus mexicana},
\textit{Eriogonum spp.}, \textit{Baccharis spp.}, \textit{Salvia
  spp}. and others \citep[Fig.~S1][]{menz-2010-4, kremen-2015-602,
  mgonigle-2015-x}. The mean distance between monitoring sites was
$15$ km, and the minimum distance between sites sampled in the same
year was 1 km.  The entire area surveyed spanned almost $300$
km$^2$. The crop fields adjacent to all sites were similarly managed
as intensive, high-input monoculture.

Monitoring of assembling hedgerows began in 2006 and continued through
2014. Surveys of these sites began the year before the area was
restored. For logistical reasons, no sampling of assembling hedgerows
was conducted in 2010. Sites were sampled between two and five times
per year (Tables S1-S3, mean $3.4$ samples per year). In each round of
sampling, the order in which sites were sampled was
randomized. Surveys were conducted under sunny conditions when the
temperature was above $21^{\circ}\mathrm{C}$ and wind speed was below
$2.5$ meters/second.

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by hive
placement by bee-keepers. All other insect flower visitors that
touched the reproductive parts of the flower were collected; however,
here we focus only on wild bees and syrphids --- the most abundant and
effective pollinators in the system (representing 49 and 19 percent of
records, respectively, C.~Kremen, A.~Klein and L.~Morandin,
unpublished data). Bee and syrphid specimens were identified to
species (or morpho-species for some bee specimens in the genera
\textit{Nomada} and \textit{Sphecodes}) by expert taxonomists.

Quantitative networks were generated for each site through time. To
account for the unequal number of surveys between years (Tables
S1-S3), we use the mean of the interactions between a pair of plants
and pollinators across surveys within a year to represent interaction
frequency.

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of modules (also called compartments). Change point
detection methods have yet to be generalized to quantitative networks,
so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative structure patterns at all
scales in the network \citep{peel2014detecting}. A network $G$ is
composed of vertices $V$ and edges $E$. The GHRG model decomposes the
$N$ vertices into a series of nested groups, the relationships among
which are represented by the dendrogram $T$. The tips of $T$ are the
vertices of $G$, and the probability that two vertices $u$ and $v$
connect is given by the parameter $p_r$. The probability distribution
of the network $G$ is thus defined as:

\begin{equation}
  \label{eq:lik}
  P(G|T,{pr}) = p_r^{E_r}(1-p_r)^{N_r-E_r}
\end{equation}
% 
Where $E_r$ is the observed number of edges between vertices with the
common ancestor $r$, and $N_r$ is the total possible edges.

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we use Bayes factors to compare the fit of two models --- one
where a change point occurred between two networks, and one where no
change occurred. We chose a sliding window of length, $w$, of four,
within which to find change points. Larger windows allow for more
gradual changes, and four was the maximum possible with our eight
years of data. Lastly, to calculate a $p$-value for the Bayes factors,
we use parametric bootstrapping to numerically estimate the null
distribution \citep{peel2014detecting}. We employed code published
online by L.~Peel for the change point analysis. Analyses were
conducted in Python 3.4.

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trials, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type
\citep{lme4}. We used standard techniques to determine whether the
assumptions of the models were met for this and all subsequent
models. For the non-assembling hedgerows and weedy field margins, only
sites with five or greater survey years were included in this analysis
(N=11). All statistical analyses were conducted in R 3.2.3 \citep{R}.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their
position and thus contribute more strongly to network
reorganization. We test whether the more persistent species with the
highest degree (number of different interaction partners) are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher the closeness centrality. We use
linear mixed models to test whether the species closeness variability
(log) is related to the persistence or degree of that species
\citep{lme4, lmetest}. We included random effects for species and
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.071$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality, as would
be expected with assembly by preferential attachment, would also lead
to high variability in closeness scores, we also test whether log
closeness centrality increases through time.

@@

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, we estimated turnover across years at a site. We first
calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using the Chao
dissimilarity estimator that incorporates abundances, while also
accounting for unobserved records \citep{chao-2005-148}. Dissimilarity
estimates can be affected by the total number of species and
individuals sampled at a site \citep[e.g.,][]{ponisio2015farm}. For
example, the probability that two sites do not share any species is
higher when there are few individuals at those sites. Following
\cite{ponisio2015farm}, we use null models that constrained species
richness to estimate the deviation of the observed dissimilarity from
that which would be expected under a random community assembly
process. With the corrected dissimilarity values, we then calculated
the multivariate dispersion of community composition across years
\citep{anderson-2011-19}. In order to test whether assembling
hedgerows had more species and interactions turnover than
non-assembling communities, the species and interaction temporal
turnover estimates were modeled as responses in a linear mixed model
with site type as an explanatory variable and site as a random effect
\citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species (Fig.~
S2). We develop a method to examine the temporal turnover of
interactions with weightings based on their similarity. We followed
the algorithm of \cite{ahn2010link} to cluster all the interactions
(edges) hierarchically across sites and years based on their
similarity, and build a dendrogram. The interaction similarity is
based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. We then
use linear mixed models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks,
including site as a random effect \citep{lme4, lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- would decrease as new, specialist species,
preferentially attach to the core. Lastly, the overall level of
network specialization may change as the community
assembles. Network-level specialization will increase if specialist
species colonize the network or species begin to limit their
interaction niche breath as the network assembles
\citep{bluthgen-2006-9}.

>>>>

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage[numbers,sort&compress]{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{xr}
\externaldocument{SI}
\usepackage{url}
\usepackage{rotating}

\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

@@

\def\title{Major network reorganizations punctuate the assembly of
  plant-pollinator communities}

\def\author{Lauren C.\
  Ponisio$^{1,2,3}$, Marilia P. Gaiarsa$^4$, Claire Kremen$^1$}

\def\runninghead{Plant-pollinator network assembly}
\def\keywords{community assembly, change points, robustness,
  nestedness, modularity, bipartite, preferential attachment}

\def\extras{
  \begin{itemize}
  \item Submitted as a Letter
  \item Abstract word count: 148
  \item Main text word count: 4967
  \item Number of references: 65
  \item Number of figures: 6
  \item Author contributions: CK designed the study, LCP and CK
    collected data, LCP and MPG analyzed output data.  LCP wrote the
    first draft of the manuscript, and all authors contributed to
    revisions.
  \item Data accessibility statement: Data will de depositied in Dryad
    upon publication
  \end{itemize}
}

@@

\begin{abstract}  
  As the world continues to lose species at an alarming rate,
  anticipating a community's ability to resist collapse will depend on
  the strength of interaction networks. We know little, however, about
  how to re-assemble interacting communities through restoration, or
  the process of ecological network assembly more generally. Using an
  eight-year dataset comprising nearly $20,000$ pollinator visitation
  records, we explore the assembly of plant-pollinator communities at
  native plant restorations sites in an agricultural landscape. We
  find that species occupy highly dynamic network positions through
  time, causing the community assembly process to be punctuated by
  major network reorganizations. In contrast, the non-assembling
  networks do not restructure as frequently. The most persistent and
  generalized species are also the most variable in their network
  positions, contrary to what is expected by assembly following
  preferential attachment --- a widly supported assembly
  mechanism. Our results fundamentally alter our understanding of how
  communities assembly and how species interactions change through
  time while helping to inform efforts to re-assembly robust
  communities through restoration.
\end{abstract}

@@

%% introduce mutualisms, restoration, network assembly
When a species goes extinct, more than a species is lost. That species
interacted with other species in its community, likely in ways that
were important or even crucial to others' survival. When a community
--- a unique combination of interacting species --- loses one species,
the system becomes weaker. Global change has created a severe
biodiversity crisis, and as species are lost, so are their
interactions \citep{dunn2009sixth, barnosky2011has}. A community's
ability to resist collapse will depend on the strength of each
interaction network \citep{Memmott2004, Rezende2007, Bascompte2009,
  Thebault2010}. To safeguard ecological function, it has become
increasingly imperative to aid the recovery of lost interactions and
component biodiversity and by facilitating the assembly of robust
interaction networks via ecological restoration
\citep{menz-2010-4}. However, we know very little about how ecological
networks assemble in general, rendering restoration of interacting
communities quite difficult.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)

Preferential attachment, the most widely explored mechanism of network
assembly, predicts that species entering a network are more likely to
interact with species that are already well-connected \citep[the
``rich-get-richer'' principle,][]{barabasi1999emergence}. In
pollination systems --- a particularly ubiquitous mutualism
\citep{ollerton-2011-321, klein-2007-303} --- some studies have found
support for this assembly mechanism. Investigating the day-to-day,
temporal assembly of a plant-pollinator network within a season,
\cite{Olesen2008} found that phenologically new plant and pollinator
species tended to interact with already well-connected species,
potentially because these species are either more abundant or
temporally persistent. Using a space-for-time substitution to study
primary succession, \cite{albrecht2010plant} also found evidence that
assembly along a glacier foreland occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}. An increase
in nestedness could have occurred via the preferential attachment
process, whereby specialist species attach to the well-connected,
generalist core.

Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[the ``rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that phenologically new plant and pollinator species tended to
interact with already well-connected species, potentially because
these species are either more abundant or more temporally
persistent. In addition, using a space-for-time substitution to study
primary succession along a glacier foreland, \cite{albrecht2010plant}
also found some evidence that assembly occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}. An
increase in nestedness could result from the preferential attachment
process where specialist species attach to the well-connected,
generalist core.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the network build-up described by preferential
attachment, significant reorganizations of interactions can also
punctuate assembly \citep{peel2014detecting}. Such significant
reorganizations of interactions, or network changing points, are
observed in social networks that respond to abrupt shifts in the
behavior of interactors \citep{peel2014detecting}. A change point is
caused by a merge, split, fragmentation or formation of modules within
a network. In ecological communities, such shifts may occur if, as new
species colonize, resident species change their interaction partners
to optimize their foraging effort. In plant-pollinator communities,
theory predicts that pollinators optimize their use of floral
resources to reduce interspecific competition and improve resource-use
efficiency \citep{pyke1984optimal, valdovinos2010consequences,
  valdovinos2013adaptive, albrecht2010plant, Bluthgen2007}. No
studies, however, have examined if network changing points occur
during ecological network assembly and/or how these changes relate to
species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially ``applied succession''
\citep[e.g.,][]{parker1997scale}.  In pollination systems, time has
been shown to affect the structure of networks in restored areas
\citep{forup-2008-742, devoto2012understanding}, suggesting that
interactions change as a community develops. Facilitating network
restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination in agricultural landscapes. To promote pollinator services
in agriculture, some farmers plant strips of native plants along farm
edges (hedgerows).  By providing habitat, hedgerows augment the
richness, abundance and trait diversity of pollinators in agricultural
landscapes \citep{morandin-2013-829, kremen-2015-602,
  ponisio2015farm}, and promote the persistence and colonization of
floral resource specialists \citep{mgonigle-2015-x}. As the community
assembles, it is important to understand how these new species are
incorporated into the network as well as the consequences of adding
species for interaction patterns and robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine-year
dataset of plant-pollinator community assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California’s Central Valley. We first
determine whether the mechanism underlying network assembly represents
a buildup of interactions as would be predicted by preferential
attachment or significant reorganizations of interactions (i.e.,
network changing points). Even with changing points in interaction
organization, networks could still assemble via preferential
attachment if the network reorganizations were primarily driven by
peripheral, temporally variable species while a stable, well-connected
core of species persist. Therefore, we tested whether the species that
are most variable in their network position --- and thus important
contributors to network reorganizations -- are less persistent and
connected species. To further explore the mechanisms underlying the
temporal dynamics of the networks, also we examine patterns in the
species and interaction temporal turnover. Finally, we investigate
whether networks assemble toward predictable interaction patterns, and
the ramifications for the robustness of the networks.

@@

Study sites were located in the Central Valley of California in Yolo,
Colusa and Solano Counties. This area is composed of intensively
managed agriculture --- primarily monocultures of conventional row
crops, vineyards and orchards. Hedgerows border large
(ca. $30$-hectare) crop fields and measured between $3-6$ m wide and
approximately $350$ m long. Hedgerows consist of native, perennial,
shrub and tree plantings \citep[Fig.~S1, ][]{menz-2010-4,
  kremen-2015-602, mgonigle-2015-x}.

We selected five farm edges to be restored as hedgerows. We monitored
those locations before the hedgerow was planted, and tracked the
assembly of the community for up to seven years as the hedgerow
matured (from $2006-2014$). For controls, we concurrently monitored
non-assembling communities within mature hedgerows (greater than $10$
years since planting, $N=29$) and unrestored, weedy field margins
($N=19$). The mean distance between monitoring sites was $15$ km, and
the minimum distance between sites sampled in the same year was $1$
km. The entire area surveyed spanned almost $300$ $km^2$. The crop
fields adjacent to all sites were similarly managed as intensive,
high-input monoculture.

Sites were sampled between two and five times per year (Tables S1-S3,
mean $3.4$ samples per year). In each round of sampling, the order in
which sites were sampled was randomized. Surveys were conducted under
sunny conditions when the temperature was above $21^{\circ}\mathrm{C}$
and wind speed was below $2.5$ meters/second.

During each sampling round, flower-visitors to plants in assembling
hedgerows and non-assembling controls were netted for one hour of
active search time (the timer was paused when handling specimens). The
identify of the plant being visited was recorded for each floral
visitor. Honeybees (\textit{Apis mellifera}) were not collected
because their abundance is determined largely by hive placement by
bee-keepers. All other insect flower visitors that touched the
reproductive parts of the flower were collected; however, here we
focus only on wild bees and syrphids --- the most abundant and
effective pollinators in the system (representing 49 and 19 percent of
records, respectively, C.~Kremen, A.~Klein and L.~Morandin,
unpublished data). Bee and syrphid specimens were identified to
species (or morpho-species for some bee specimens in the genera
\textit{Nomada} and \textit{Sphecodes}) by expert taxonomists.

Quantitative networks were generated for each site through
time. Because the nuber of sampling rounds varied between years
(Tables S1-S3), we used the mean of the interactions between a pair of
plants and pollinators within a year to represent interaction
frequency.

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. Change point detection methods have yet to be generalized to
quantitative networks, so for this analysis we focused on qualitative
(binary) networks. Following \cite{peel2014detecting}, we first
defined a probability distribution over the networks using the
generalized hierarchical random graph model (GHRG). The GHRG model
captures both assortative and disassortative structure patterns at all
scales in the network \citep{peel2014detecting}. A network $G$ is
composed of vertices $V$ and edges $E$. The GHRG model decomposes the
$N$ vertices into a series of nested groups, the relationships among
which are represented by the dendrogram $T$. The tips of $T$ are the
vertices of $G$, and the probability that two vertices $u$ and $v$
connect is given by the parameter $p_r$. The probability distribution
of the network $G$ is thus defined as:

\begin{equation}
  \label{eq:lik}
  P(G|T,{pr}) = p_r^{E_r}(1-p_r)^{N_r-E_r}
\end{equation}
% 
Where $E_r$ is the observed number of edges between vertices with the
common ancestor $r$, and $N_r$ is the total possible edges, and the
rest of the notation is described above.

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we use Bayes factors to compare the fit of two models --- one
where a change point occurred between two networks, and one where no
change occurred. We chose a sliding window of length, $w$, of four
years to detect change points. Larger windows allow for more gradual
changes, and four was the maximum possible with our eight years of
data. Lastly, to calculate a $p$-value for the Bayes factors, we use
parametric bootstrapping to numerically estimate the null distribution
\citep{peel2014detecting}. We employed code published online by
L.~Peel for the change point analysis. Analyses were conducted in
Python 3.4.

We next tested whether the change points occurring in maturing
hedgerows were a component of the assembly process or a product of
environmental shifts that lead to network reorganizations in all types
of communities. We modeled the number of change points as successes
and the total number of sample years at each site as trials, and used
a generalized linear model with Binomial error to test whether the
probability of a change point occurrence varied by site type. We used
standard techniques to determine whether the assumptions of the models
were met for this and all subsequent models. For the non-assembling
controls, only sites with five or greater survey years were included
in this analysis ($N=11$). All statistical analyses were conducted in
R 3.2.3 \citep{R}.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remained in relatively similar network
positions through time, whereas others were more variable in their
position and thus contributed more strongly to network
reorganization. We tested whether the more persistent species with the
highest degree (number of different interaction partners) were the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

We calculated species persistence as the proportion of surveys in
which a plant or pollinator is observed. Species observed consistently
within and between years were thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher the closeness centrality. We used
linear mixed models to test whether the species closeness variability
(log) is related to the persistence or degree of that species
\citep{lme4, lmetest}. We included random effects for species and
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.071$, $p$-value $<$ $2*10^{-16}$), we included
each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we used the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality --- as
would be expected with assembly by preferential attachment --- we also
tested whether log closeness centrality increases through time.

@@

To estimate the temporal species and interaction turnover, we used an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, we estimated turnover across years at a site. We first
calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using the Chao
dissimilarity estimator that incorporates abundances, while also
accounting for unobserved records \citep{chao-2005-148}. Dissimilarity
estimates can be affected by the total number of species and
individuals sampled at a site \citep[e.g.,][]{ponisio2015farm}. For
example, the probability that two sites do not share any species is
higher when there are few individuals at those sites. Following
\cite{ponisio2015farm}, we used null models that constrained species
richness to estimate the deviation of the observed dissimilarity from
that which would be expected under a random community assembly
process. With the corrected dissimilarity values, we then calculated
the multivariate dispersion of community composition across years
\citep{anderson-2011-19}. In order to test whether assembling
hedgerows had more species and interactions turnover than
non-assembling communities, the species and interaction temporal
turnover estimates were modeled as responses in a linear mixed model
with site type as an explanatory variable and site as a random effect
\citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~\ref{fig:methods}). We developed a method to examine the
temporal turnover of interactions with weightings based on their
similarity. We followed the algorithm of \cite{ahn2010link} to cluster
all the interactions (edges) hierarchically across sites and years
based on their similarity, and build a dendrogram. The interaction
similarity is based how many plants and pollinators (vertices) two
edges share \citep{ahn2010link, kalinka2011linkcomm}. The more species
edges shared in common, the shorter the branch length between them on
the dendrogram.  We next calculated the temporal turnover of
interactions weighted by their similarity, as approximated by
``phylogenetic'' distance \citep{graham2008phylogenetic,
  picante-2010-1463}. We then used linear mixed models to test whether
the weighted turnover of interactions varied between assembling and
non-assembling networks, including site as a random effect
\citep{lme4, lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- would decrease as new, specialist species,
preferentially attach to the core. Finally, the overall level of
network specialization may change as the community
assembles. Network-level specialization will increase if specialist
species colonize the network or species begin to limit their
interaction niche breath as the network assembles
\citep{bluthgen-2006-9}.
